---
title: "Model Accuracy"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(kableExtra)
```

This document reports our estimates of the accuracy of the six models that produce our transparency classifications. The estimates are calculated using 3-fold cross calidation. 


The three indicators are as follows:

  - *accuracy*: proportion of labels that are correctly classified. 
  - *negative predictive value*: proportion of towns labeled with a 0  with a ground truth of 0. 
  - *positive predictive value*: proportion of towns labeled with a 1 with a ground truth of 1.


```{r, load_models, warning=FALSE, include=TRUE, message=FALSE}
drake::loadd(bdg_mod)
drake::loadd(agd_mod)
drake::loadd(bid_mod)
drake::loadd(cafr_mod)
drake::loadd(min_mod)
drake::loadd(rec_mod)

drake::loadd(labels)
baseline_labels <- labels %>%
  group_by(variable) %>%
  summarise(Baseline = round(mean(label, na.rm = TRUE), 2)) %>%
  rename(Indicator = variable)
```

## Accuracy

```{r table,  message=FALSE, warning=FALSE, include=TRUE}
ppv <- bind_rows(filter(bdg_mod$cv_metrics, .metric == "ppv"),
          filter(agd_mod$cv_metrics, .metric == "ppv"),
          filter(bid_mod$cv_metrics, .metric == "ppv"),
          filter(cafr_mod$cv_metrics, .metric == "ppv"),
          filter(min_mod$cv_metrics, .metric == "ppv"),
          filter(rec_mod$cv_metrics, .metric == "ppv")) %>%
  select(mean) %>%
  mutate(Indicator = c("BDG", "AGD", "BID", "CAFR", "MIN", "REC"),
         PPV  = round(mean, 2)) %>%
  select(-mean)

npv <- bind_rows(filter(bdg_mod$cv_metrics, .metric == "npv"),
          filter(agd_mod$cv_metrics, .metric == "npv"),
          filter(bid_mod$cv_metrics, .metric == "npv"),
          filter(cafr_mod$cv_metrics, .metric == "npv"),
          filter(min_mod$cv_metrics, .metric == "npv"),
          filter(rec_mod$cv_metrics, .metric == "npv")) %>%
  select(mean) %>%
  mutate(Indicator = c("BDG", "AGD", "BID", "CAFR", "MIN", "REC"),
         NPV  = round(mean, 2)) %>%
  select(-mean)


bind_rows(filter(bdg_mod$cv_metrics, .metric == "accuracy"),
          filter(agd_mod$cv_metrics, .metric == "accuracy"),
          filter(bid_mod$cv_metrics, .metric == "accuracy"),
          filter(cafr_mod$cv_metrics, .metric == "accuracy"),
          filter(min_mod$cv_metrics, .metric == "accuracy"),
          filter(rec_mod$cv_metrics, .metric == "accuracy")) %>%
  select(mean) %>%
  mutate(Indicator = c("BDG", "AGD", "BID", "CAFR", "MIN", "REC"),
         Accuracy  = round(mean, 2)) %>%
  select(-mean) %>%
  left_join(baseline_labels) %>%
  left_join(ppv) %>% 
  left_join(npv) %>%
  select(Indicator, Baseline, Accuracy, PPV, NPV) %>%
  kable() 

```

